Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-25 paper.tex
9.75
Fixed author list.

    % Note: For CCS submission we need to have it anonymous
    % The author list will be:
    % Sai, Pierre-Marie, Giovanni, Ziming, Adam, Gail

	\author{
		% You can go ahead and credit any number of authors here,
		% e.g. one 'row of three' or two rows (consisting of one row of three
		% and a second row of one, two or three).
		%
		% The command \alignauthor (no curly braces needed) should
		% precede each author name, affiliation/snail-mail address and
		% e-mail address. Additionally, tag each line of
		% affiliation/address with \affaddr, and tag the
		% e-mail address with \email.
		%
		% 1st. author
		%% \alignauthor
		%% Sai Prashanth Chandramouli\\
		%% \affaddr{Arizona State University}\\
		%% \email{saipc@asu.edu}
		%% % 2nd. author
		%% \alignauthor
		%% Adam Doup\'{e}\titlenote{The secretary disavows
		%% 	any knowledge of this author's actions.}\\
		%% \affaddr{Arizona State University}\\
		%% \email{doupe@asu.edu}
		%% % 3rd. author
		%% \alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
		%% 	one who did all the really hard work.}\\
		%% \affaddr{The Th{\o}rv{\"a}ld Group}\\
		%% \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
		%% \affaddr{Hekla, Iceland}\\
		%% \email{larst@affiliation.org}
		%% \and  % use '\and' if you need 'another row' of author names
		%% % 4th. author
		%% \alignauthor Lawrence P. Leipuner\\
		%% \affaddr{Brookhaven Laboratories}\\
		%% \affaddr{Brookhaven National Lab}\\
		%% \affaddr{P.O. Box 5000}\\
		%% \email{lleipuner@researchlabs.org}
		%% % 5th. author
		%% \alignauthor Sean Fogarty\\
		%% \affaddr{NASA Ames Research Center}\\
		%% \affaddr{Moffett Field}\\
		%% \affaddr{California 94035}\\
		%% \email{fogartys@amesres.org}
		%% % 6th. author
		%% \alignauthor Charles Palmer\\
		%% \affaddr{Palmer Research Laboratories}\\
		%% \affaddr{8600 Datapoint Drive}\\
		%% \affaddr{San Antonio, Texas 78229}\\
		%% \email{cpalmer@prl.com}
	}
	% There's nothing stopping you putting the seventh, eighth, etc.
	% author on the opening page (as the 'third row') but we ask,
	% for aesthetic reasons that you place these 'additional authors'
	% in the \additional authors block, viz.
	%% \additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
	%% 	email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
	%% 	(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
	%% \date{30 July 1999}
	% Just remember to make sure that the TOTAL number of authors
	% is the number that will appear on the first page PLUS the
	% number that will appear in the \additionalauthors section.

	\maketitle
	\input{abstract}

>>>>

    % Note: For CCS submission we need to have it anonymous
    % The author list will be:
    % Sai, Pierre-Marie, Chris, Giovanni, Ziming, Adam, Gail

	\author{
		% You can go ahead and credit any number of authors here,
		% e.g. one 'row of three' or two rows (consisting of one row of three
		% and a second row of one, two or three).
		%
		% The command \alignauthor (no curly braces needed) should
		% precede each author name, affiliation/snail-mail address and
		% e-mail address. Additionally, tag each line of
		% affiliation/address with \affaddr, and tag the
		% e-mail address with \email.
		%
		% 1st. author
		\alignauthor
		Sai Prashanth Chandramouli$^\dag$, Pierre-Marie Bajan$^\S$, Christopher Kruegel$^\ddag$, Giovanni Vigna$^\ddag$, Ziming Zhao$^\dag$, Adam Doup\'e$^\dag$, and Gail-Joon Ahn$^\dag$\\
		\affaddr{Arizona State University$^\dag$, IRT SystemX and the Telecom SudParis$^\S$, and University of California, Santa Barbara$^\ddag$}\\
		\{saipc, zzhao30, doupe, gahn\}@asu.edu$^\dag$,
        pierre-marie.bajan@irt-systemx.fr$^\S$, \\
        \{chris, vigna\}@cs.ucsb.edu$^\ddag$
        }
		% 2nd. author
		%% \alignauthor

		%% \affaddr{University of California, Santa Barbara}\\
		%% pm.bajan@free.fr
		%% \alignauthor
		%% \\
		%% \affaddr{University of California, Santa Barbara}\\
		%% giovanni.vigna@gmail.com
		%% \and
		%% \alignauthor
		%% \\
		%% \affaddr{Arizona State University}\\
		%% Ziming.Zhao@asu.edu
		%% \alignauthor
		%% Adam Doup\'{e}\\
		%% \affaddr{Arizona State University}\\
		%% doupe@asu.edu
		%% \alignauthor
		%% Gail-Joon Ahn\\
		%% \affaddr{Arizona State University}\\
		%% Gail-Joon.Ahn@asu.edu
		% 3rd. author
		%% \alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
		%% 	one who did all the really hard work.}\\
		%% \affaddr{The Th{\o}rv{\"a}ld Group}\\
		%% \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
		%% \affaddr{Hekla, Iceland}\\
		%% \email{larst@affiliation.org}
		%% \and  % use '\and' if you need 'another row' of author names
		%% % 4th. author
		%% \alignauthor Lawrence P. Leipuner\\
		%% \affaddr{Brookhaven Laboratories}\\
		%% \affaddr{Brookhaven National Lab}\\
		%% \affaddr{P.O. Box 5000}\\
		%% \email{lleipuner@researchlabs.org}
		%% % 5th. author
		%% \alignauthor Sean Fogarty\\
		%% \affaddr{NASA Ames Research Center}\\
		%% \affaddr{Moffett Field}\\
		%% \affaddr{California 94035}\\
		%% \email{fogartys@amesres.org}
		%% % 6th. author
		%% \alignauthor Charles Palmer\\
		%% \affaddr{Palmer Research Laboratories}\\
		%% \affaddr{8600 Datapoint Drive}\\
		%% \affaddr{San Antonio, Texas 78229}\\
		%% \email{cpalmer@prl.com}
	% There's nothing stopping you putting the seventh, eighth, etc.
	% author on the opening page (as the 'third row') but we ask,
	% for aesthetic reasons that you place these 'additional authors'
	% in the \additional authors block, viz.
	%% \additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
	%% 	email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
	%% 	(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
	%% \date{30 July 1999}
	% Just remember to make sure that the TOTAL number of authors
	% is the number that will appear on the first page PLUS the
	% number that will appear in the \additionalauthors section.
	\renewcommand{\email}{e-\nobreak{}mail\xspace}
	\maketitle
	\input{abstract}
